%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {The Capogreco Group - Datatize Co.Ltd} % Organization
    {Da Nang, Vietnam} % Location
    {May 2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Python - Dash(Flask) and Javascript - ReactJS framework to build the Data Visualization Systems.}
        \item {Worked with Airflow tools, config schedule tasks.}
        \item {Built company website with ReactJS.}
        \item {Setup project as microservice with Docker and docker-compose.}
        \item {Setup CI/CD pipelines for all projects.}
        \item {Built monitoring, logging server to track other server.}
        \item {Worked with Cloud Provider like AWS, GCP and Azure.}
        \item {Main skills:
        	\begin{itemize}
            \item {Language: Python, Javascript, Bash script}
            \item {Framework: Dash/Flask, ReactJS}
            \item {Cloud:}
            	\begin{itemize}
                \item {AWS: IAM, EC2, VPC, Route 53, SES, ACM}
                \item {Azure: Virtual Machine, Container Registry, Container Instance, Kubernetes Service}
                \item {GCP: Computer Engine, Cloud SQL, Cloud Storage, Secret Manager, Kubernetes Engine }
			        \end{itemize}
        \item {OS: Mac, Linux, Windows}
        \item {CI/CD: Gitlab CI, Github Action}
			\end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
\cventry
  {Freelancer} % Job title
  {Fullstack Developer} % Organization
  {Da Nang, Vietnam} % Location
  {Dec 2021 - present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked with Python - Django framework to write API.}
      \item {Work with ReactJS to build frontend website.}
      \item {Implement eKYC system, payment system,...}
      \item {Main skills:
        \begin{itemize}
          \item {Language: Python, Javascript}
          \item {Framework: Django, ReactJS}
          \item {Docker}
        \end{itemize}
      }
    \end{cvitems}
  }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {D-soft, JSC.} % Organization
    {Da Nang, Vietnam} % Location
    {May 2019 - Aprl 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed web application tool to manage the IoT Device, Business System (Orders, Inventory, Warehouse).}
        \item {Developed web application tool to Debuging for AI system, Dashboard for Face Recognize System.}
        \item {Implemented API microservice in Django, Flask.}
        \item {R\&D about Microsoft Azure.}
        \item {Built automated CI/CD pipelines on Gitlab CI, Github Action for containerized application using Docker, Azure Container Registry and deployed onto Azure Kubernetes Service.}
        \item {Main skills:
        	\begin{itemize}
        		\item {Language: Python, Javascript, PHP, Bash}
  				\item {Framework: Django, Flask, Express, Laravel, ReactJS, VueJS}
				\item {OS: Mac, Linux}
  				\item {Docker}
  				\item {Azure Cloud: Azure K8S Service, Azure Container Registry, Azure Storage, Azure IoT hub}
  				\item {CI/CD: Gitlab CI, Github Action}
			\end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {PhuQuoc Market} % Organization
    {Da Nang, Vietnam} % Location
    {March 2020 - Oct 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coding backend system for mobile app.}
        \item {Implement RabitMQ, ZaloPay.}
        \item {Dockerize and deploy onto Digital Ocean VPS.}
        \item {Main skills:
        	\begin{itemize}
        		\item {Language: Typescript}
  				\item {Framework: Loopback 4}
  				\item {Docker}
			\end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intership} % Job title
    {GMO-Z VietNamLab Center} % Organization
    {Da Nang, Vietnam} % Location
    {Jan 2019 - March 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed web application Japanse Examination System like tryjlpt.com.}
        \item {Built automated using Ansible-Docker.}
        \item {Main skills:
        	\begin{itemize}
        		\item {Language: PHP}
  				\item {Framework: Yii2}
  				\item {Ansible, Docker}
			\end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}