%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Software Engineer} % Job title
    {Saigon Technology} % Organization
    {Da Nang, Vietnam} % Location
    {Nov 2022 - Oct 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with American clients to build the data pipeline system using Airflow.}
        \item {Developed and maintained Airflow DAGs for seamless data processing from various services and generation of comprehensive reports.}
        \item {Developed a system to detect and recognize employees, collect employees' data, and support internal timekeeping systems}
        \item {Performed requirement analysis and collaborated with the team to design the software architecture for the application.}
        \item {Set up ELK to optimize searching queries and monitor the logging}
        \item {Set up Kafka to consume real-time messages}
        \item {Set up CI/CD using the Bitbucket pipeline to deploy the system automatically.}
        \item {Technologies:
          \begin{itemize}
            \item {Language: Python, Javascript, Bash}
            \item {Framework: Django, Flask, ReactJS}
            \item {Tools: Airflow, ELK, Kafka, Docker}
            \item {Deploy: AWS, On-Premise}
            \item {CI/CD: Bitbucket pipeline, AWS CodeBuild, AWS CodePipeline, AWS CodeDeploy}
          \end{itemize}
        }
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
    \cventry
    {Software Engineer \& Quantitative Developer} % Job title
    {Datatize} % Organization
    {Singapore} % Location
    {May 2021 - Oct 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters in development.}
        \item {Designed and provisioned the entire system infrastructure.}
        \item {Worked with Python - Dash(Flask) to build the Live Trading and Data Visualization Systems.}
        \item {Supported build trading strategies, backtesting result.}
        \item {Used ReactJS to build extra components for Dash.}
        \item {Developed Airflow DAGs for crawl and process data from several crypto exchanges like Binance, FTX, Deribit,...}
        \item {Implemented several API microservices.}
        \item {Developed a real-time chatting system using Websocket, Firebase; push notification to mobile devices.}
        \item {Deployed a centralized logging environment(ELK) that gathers log data from docker containers.}
        \item {Provisioned a dashboard using Grafana - Prometheus to visualize and monitor the resources of the server.}
        \item {Set up self-hosted SonarQube to analyze code and scan vulnerabilities.}
        \item {Set up CI/CD using the GitHub Action to automatically deploy the system.}
        \item {Technologies:
          \begin{itemize}
            \item {Language: Python, Javascript, Bash}
            \item {Framework: Dash, ReactJS, }
            \item {Tools: Airflow, ELK, Grafana, SonarQube, Docker}
            \item {Deploy: GCP, On-Premise}
            \item {CI/CD: GitHub Action}
          \end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Freelancer} % Job title
    {Crypto Subscriptions} % Organization
    {United States} % Location
    {Dec 2021 – Jul 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the Django backend server to create a robust and scalable RESTful API, ensuring efficient data processing and seamless integration with client applications.}
        \item {Conducted research and successfully implemented KYC (Know Your Customer) and MFA (Multi-Factor Authentication) functionalities to enhance system security and compliance.}
        \item {Integrated payment systems, Wyre and Plaid, enabling seamless and secure payment transactions within the application.}
        \item {Developed the ReactJS Front-End, and created dynamic UI to ensure an outstanding UX.}
        \item {Designed and implemented a cron job to handle subscriptions efficiently.}
        \item {Technologies:
            \begin{itemize}
                \item {Backend: Python, Django, Django Rest Framework.}
                \item {Frontend: Javascript, React JS, HTML, CSS.}
                \item {Database: PostgreSQL.}
                \item {MFA: Twilio Authy.}
                \item {E-KYC systems: Persona, Sumsub.}
                \item {Payment systems: Wyre, Plaid.}
            \end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Freelancer DevOps} % Job title
    {NFT Marketplace} % Organization
    {Da Nang, VietNam} % Location
    {Sep 2021 - Jan 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with the development team to deploy the application on AWS.}
        \item {Utilized Terraform to set up and manage the project's infrastructure architecture on AWS. Set up AWS S3 for Storage, SES for sending Email, Route53 for DNS, and VPC for public and private networks.}
        \item {Configured GitLab CI for a CI/CD pipeline, integrating it with Terraform for automated builds and deployments.}
        \item {Technologies:
            \begin{itemize}
                \item {Language: Bash.}
                \item {Infra as Code: Terraform.}
                \item {CI/CD: Gitlab CI.}
                \item {Cloud: AWS.}
            \end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Software Engineer} % Job title
    {D-soft, JSC.} % Organization
    {Da Nang, Vietnam} % Location
    {March 2019 - Apr 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed web application tool to manage the IoT Device and Business System (Orders, Inventory, Warehouse import and export).}
        \item {Developed web application tool to Debugging for AI system, Dashboard for Face Recognize System.}
        \item {Implemented API microservice in Django, Flask.}
        \item {R\&D about Microsoft Azure.}
        \item {Built automated CI/CD pipelines on Gitlab CI, GitHub Action for containerized applications using Docker, Azure Container Registry and deployed onto Azure Kubernetes Service.}
        \item {Technologies:
            \begin{itemize}
                \item {Language: Python, Javascript, PHP, Bash}
                \item {Framework: Django, Flask, Express, Laravel, ReactJS, VueJS}
                \item {OS: Mac, Linux}
                \item {Docker}
                \item {Azure Cloud: Azure K8S Service, Azure Container Registry, Azure Storage, Azure IoT hub}
                \item {CI/CD: Gitlab CI, GitHub Action}
            \end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Intership} % Job title
    {GMO-Z VietNamLab Center} % Organization
    {Da Nang, Vietnam} % Location
    {Jan 2019 - March 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed web application Japanse Examination System like tryjlpt.com.}
        \item {Built automated using Ansible-Docker.}
        \item {Main skills:
            \begin{itemize}
                \item {Language: PHP}
                \item {Framework: Yii2}
                \item {Ansible, Docker}
            \end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
